The 2- and 3-point surface correlation functions calculations: from novel exact continuous approach to improving methodology for discrete images

### 2023-05-12 paper.tex
Change document class

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[inline]{enumitem}
\usepackage{resizegather}

@@

\begin{document}
\preprint{APS/123-QED}

\author{Vasily Postnicov\textsuperscript{1}}
\author{Marina V. Karsanina\textsuperscript{1}}
\author{Aleksey Khlyupin\textsuperscript{1,2}}
\author{Kirill M. Gerke\textsuperscript{1}}
\email{kg@ifz.ru}

\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
  Russian Academy of Sciences, Moscow, 107031, Russia}
\affiliation{\textsuperscript{2}Moscow Institute of Physics and Technology,
  Dolgoprudny, 141701, Russia}
%\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
%  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}

@@

\begin{abstract}
  Surface correlation functions are extremely useful descriptors of interfaces and in this role 
  can be used in material science, rock and soil physics, food engineering and other numerous
  areas. However, their widespread usage was hampered by insufficiently robust computation methodologies. 
  In this contribution we elaborate on recent works in surface function evaluation and present a 
  novel exact algorithm to compute $F_{ss}$ and $F_{sss}$ functions for smooth boundary sets without 
  discretization. This allows us to test digital computational approach on geometries beyond those with 
  analytical solutions. Moreover, we propose a better edge detection filter that allowed to improve the 
  quality of surface correlation functions (both surface-surface and surface-void) assessment based on 
  digital images. The code for continuous and discrete computational frameworks is freely available and 
  is now the part of the more general CorrelationFunctions.jl package.
\end{abstract}
\keywords {3D images; correlation functions; surface-surface function;
  surface-void function; image analysis; image scaling}

>>>>

\documentclass[preprint]{elsarticle}

%\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}
\usepackage{hyperref}
\usepackage[inline]{enumitem}
\usepackage{resizegather}
\usepackage{cleveref}

@@

\bibliographystyle{elsarticle-num}

\begin{document}

\author[Smith]{Vasily~Postnicov}
\author[Smith]{Marina~V.~Karsanina}
\author[Smith,MIT]{Aleksey~Khlyupin}
\author[Smith]{Kirill~M.~Gerke\corref{maincorr}}
\cortext[maincorr]{Corresponding author}
\ead{kg@ifz.ru}

\address[Smith]{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 107031, Russia}
\address[MIT]{Moscow Institute of Physics and Technology,
  Dolgoprudny, 141701, Russia}
%\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
%  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}

@@

\begin{abstract}
  Surface correlation functions are extremely useful descriptors of interfaces
  and in this role can be used in material science, rock and soil physics, food
  engineering and other numerous areas. However, their widespread usage was
  hampered by insufficiently robust computation methodologies.  In this
  contribution we elaborate on recent works in surface function evaluation and
  present a novel exact algorithm to compute $F_{ss}$ and $F_{sss}$ functions
  for smooth boundary sets without discretization. This allows us to test
  digital computational approach on geometries beyond those with analytical
  solutions. Moreover, we propose a better edge detection filter that allowed to
  improve the quality of surface correlation functions (both surface-surface and
  surface-void) assessment based on digital images. The code for continuous and
  discrete computational frameworks is freely available and is now the part of
  the more general CorrelationFunctions.jl package.
\end{abstract}

\begin{keyword}
  3D images, correlation functions, surface-surface function,
  surface-void function, image analysis, image scaling
\end{keyword}
